Software variability in fMRI analysis:\\ comparing between-tool and numerical errors

### 2021-12-06 paper/paper.tex
Edits in results

 \documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
%\usepackage{hyphenat}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage[binary-units=true]{siunitx}
\usepackage{ulem}
%\usepackage{censor}
\usepackage[table]{xcolor}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{tabularx}

@@

\begin{IEEEkeywords}
  Numerical Instability, Reproducibility, Monte-Carlo arithmetic, Neuroimaging
\end{IEEEkeywords}

@@

\section{Results}
All scripts and data to reproduce the results are
available at \url{https://github.com/big-data-lab-team/fuzzy-neurotools}.

@@

We verified the correctness of our analyses by comparing our unperturbed
t-statistic group maps with the ones obtained
in~\cite{bowring2019exploring}. For FSL, we found
identical checksums. For SPM, the checksums were different but differences
were visually unnoticeable. For AFNI, the activation maps were similar
overall, however, differences were more noticeable visually. 
The observed differences remained small and might be due to the use of
Octave vs MATLAB in SPM. We performed visual quality control of the AFNI
and SPM results for each individual subject and confirmed that images were
correctly registered to the MNI template.

\subsection{Group-level unthresholded maps}

Summary statistics for the group-level unthresholded and thresholded
t-statistics are reported in Table~\ref{table:pipeline-stats}. For each
tool pair (A, B), BT variability was significantly larger than machine
error in tool A or B, in both thresholded and unthresholded maps (Wilcoxon
signed-rank test p~\textless~$10^{-162}$ for all tests, t-test p=0 for all
tests).

% This was confirmed by computing the T-test and Wilcoxon signed-rank statistics between BT and WT as:

% \begin{equation*}
%   \left\{
%     \begin{aligned}
%       & BT(a, b), WT(a),\\
%       & BT(a, b), WT(b)
%     \end{aligned}  
%     \quad  a,b \in [FSL, SPM, AFNI] \;
%   \right\}
%   \label{eq:t-tests}
% \end{equation*}

% We obtained statistically significant values between BT and WT
% variability with t-value $> 70$ and p-value $< 0.05$.

%%%%%%%%%% Summary of statstics %%%%%%%%
\setlength{\tabcolsep}{5pt}
\begin{table}[h]
    \centering
    \begin{tabular}{cccc|cc}
        \toprule
        \multirow{2}{*}{}& {} & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c}{Unthresholded} \\
        \cmidrule{3-4} \cmidrule{5-6} \\
        {} & {} & Mean & Std. dev. & Mean & Std. dev. \\
        \midrule
        \rowcolor{lightgray}
        {Between Tools} & FSL vs. SPM        &  1.282       & 0.525      & 0.443     & 0.344  \\
        \rowcolor{lightgray}
        {(BT)} & FSL vs. AFNI                &  1.548       & 0.616      & 0.547     & 0.441  \\
        \rowcolor{lightgray}
        {} & AFNI vs. SPM                    &  1.475       & 0.672      & 0.608     & 0.477  \\
        {Within Tool} & FSL                  &  0.354       & 0.491      & 0.082     & 0.065  \\
        {(WT)}   & SPM                       &  0.252       & 0.448      & 0.054     & 0.045  \\
        {}   & AFNI                          &  0.434       & 0.524      & 0.128     & 0.135  \\
        \bottomrule
    \end{tabular}
    \caption{Voxel-wise mean and standard deviation of BT and WT variability
    in group-level t-statistics maps.}
    \label{table:pipeline-stats}
\end{table}

% \subsection{Variability of unthresholded statistical maps}

Figure~\ref{fig:unthresh-maps} compares BT and WT variability in
unthresholded maps. WT variability remains lower than BT variability
overall. Moreover, BT and WT variability appeared moderately correlated (R
in [0.56, 0.58], p=0.0). The set of voxels exhibiting comparable BT and
WT values (located around the identity line in the XY plot) does not seem to have 
any spatial consistency.

%%%%%%%%%% Var. of Unthresh %%%%%%%%
\begin{figure*}[ht]
    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
      \begin{subfigure}[ht]{\textwidth}
      \centering
      \includegraphics[width=\textwidth]{figures/std/gl-unthresh.png}
      %\caption{Standard deviation of thresholded t-statistics map on template surface}
      \end{subfigure}
      \hfill
      \begin{subfigure}[ht]{\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{figures/std-corr-unthresh-plot.png}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
      \end{subfigure}

    \caption{Unthresholded group-level variability computed between tools (\textbf{A}) and within tools (\textbf{B}),
    and difference between them (\textbf{C}).}
    \label{fig:unthresh-maps}
    \end{minipage}}
  \end{figure*}

  \subsection{Subject-level unthresholded maps}

  Summary statistics for subject-level unthresholded t-statistics maps are
  reported in Table~\ref{table:unthresh-maps-subjects}. As for group-level
  maps, BT variability was consistently larger than WT variability (Wilcoxon
  signed-rank test p~\textless~$10^{-160}$ for all tests, t-test p=0 for all
  tests).

  Figure~\ref{fig:unthresh-maps-sbj} shows BT and WT variability for
  the subject with the highest WT variability among the 16 subjects. For
  this particular subject, WT variability approaches and even surpasses BT
  variability in some regions. Besides, numerical variability appears focal.

  As for the group maps, BT and WT variability appeared moderately
  correlated for all subjects (Figure~\ref{fig:unthresh-correlation-allsbj}, 
  R in [0.442, 0.612], p=0.0 for all
  subjects).

  %%%%%%%%%% Summary of statstics %%%%%%%%
\setlength{\tabcolsep}{5pt}
\begin{table}[h]
    \centering
    \begin{tabular}{cccc}
        \toprule
        \multirow{2}{*}{}& {} & \multicolumn{2}{c}{Unthresholded} \\
        \cmidrule{3-4} \\
        {} & {} & Mean & Std. dev. \\
        \midrule
        \rowcolor{lightgray}
        {Between Tools} & FSL vs. SPM        &  0.366       & 0.293     \\
        \rowcolor{lightgray}
        {(BT)} & FSL vs. AFNI                &  0.439       & 0.352     \\
        \rowcolor{lightgray}
        {} & AFNI vs. SPM                    &  0.491       & 0.381     \\
        {Within Tool} & FSL                  &  0.077       & 0.054     \\
        {(WT)}   & SPM                       &  0.048       & 0.037     \\
        {}   & AFNI                          &  0.108       & 0.131     \\
        \bottomrule
    \end{tabular} 
    \caption{Voxel-wise mean and standard deviation of BT and WT variability
    in subject-level t-statistics maps (averages on 16 subjects).}
    \label{table:unthresh-maps-subjects}
\end{table}

  %%%%%%%%%% Var. of Unthresh sbj05%%%%%%%%
\begin{figure*}[ht]
  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
    \centering
    \includegraphics[width=\textwidth]{figures/std/sbj05-std.png}
    %\caption{Standard deviation of thresholded t-statistics map on template surface}
    \caption{For subject with highest WT variability, unthresholded subject-level variability computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).}
  \label{fig:unthresh-maps-sbj}
  \end{minipage}}
\end{figure*}

\subsection{Group-level untresholded maps at different virtual precisions}

While the previous results were obtained for machine error, we also evaluated numerical variability across different virtual precisions for FSL.
Figure~\ref{fig:across-precisions} shows the root-mean-square error (RMSE) between BT and WT variability maps.
The virtual precision of t=17 bits minimized the RMSE between BT and WT.
Figure~\ref{fig:gnp-mni} shows the corresponding BT and WT maps obtained at t=17 bits, showing 
that BT and WT reach comparable magnitudes in some regions.

  %%%%%%%%%% plot different precisions%%%%%%%%
  \begin{figure}[ht]
    \fbox{\begin{minipage}{\dimexpr \columnwidth-2\fboxsep-2\fboxrule}
        \centering
        \includegraphics[width=\columnwidth]{figures/rmse-precisions.png}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
      \caption{Voxel-wise RMSE between BT and WT variability maps for different virtual precisions.}
    \label{fig:across-precisions}
    \end{minipage}}
  \end{figure}

  %%%%%%%%%% plot different precisions%%%%%%%%
  \begin{figure*}[ht]
    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
      \begin{subfigure}[ht]{\textwidth}
        \centering
        \includegraphics[width=.75\textwidth]{figures/bg_global_precision.pdf}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
        \end{subfigure}
        \hfill
        \begin{subfigure}[ht]{\textwidth}
          \centering
          \includegraphics[width=.8\textwidth]{figures/std-corr-unthresh-vp17-plot.png}
          %\caption{Standard deviation of thresholded t-statistics map on template surface}
        \end{subfigure}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
        \caption{Unthresholded group t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).
        WT is computed at the virtual precision of t=17 bits.}
    \label{fig:gnp-mni}
    \end{minipage}}
  \end{figure*}

  \subsection{Group-level thresholded maps}

  Figure~\ref{fig:thresh-maps} compares BT and WT for thresholded group-level maps.
  While BT is consistently larger than machine error, thresholding is an unstable operation 
  that results in comparable magnitudes for BT and WT within activation clusters where BT variability is low.

  Figure~\ref{fig:cm-thresh} compares regional activation instability for BT and WT. The average ratio
  of unstable regions was 26\% for BT and 9.2\% for WT. The average F1 score in these confusion matrics was 0.28. Regional 
  WT instability appears to moderately explain BT regional BT instability.

  %%%%%%%%%% Var. of Thresh %%%%%%%%
  \begin{figure*}[ht]
      \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
        \begin{subfigure}[ht]{\textwidth}
          \centering
          \includegraphics[width=\textwidth]{figures/std/gl-thresh.png}
          %\caption{Standard deviation of thresholded t-statistics map on template surface}
          \end{subfigure}
          \hfill
          \begin{subfigure}[ht]{\textwidth}
            \centering
            \includegraphics[width=.9\textwidth]{figures/dice_analysis-plot.png}
            %\caption{Standard deviation of thresholded t-statistics map on template surface}
          \end{subfigure}
        \centering
      \caption{Thresholded group t-statistics standard deviation maps
      computed across tools (\textbf{A}) and Fuzzy Libmath samples
      (\textbf{B}). The confusion matrices of activation instability
      in BT and WT among the 360 regions from the HCP-MMP1.0 parcellation is represented in the bottom row.}
      \label{fig:thresh-maps}
      \end{minipage}}
    \end{figure*}

@@

In fMRI \emph{group analyses}, machine error remains an order of magnitude
smaller than between-tool variability. Group analyses have a regularization
effect toward numerical noise, which is expected to amplify as sample size
increases. Therefore, for fMRI studies with large sample sizes, machine
error can safely be neglected with respect to between-tool variability. The
recommendation made in~\cite{botvinik2020variability} to rely on ``multiverse" analyses where
multiple analysis tools are compared is therefore likely to successfully correct
for machine error in group studies.

@@

In \emph{subject analyses}, machine error and between-tool variabilty can
become comparable for some subjects in some regions. This observation is particularly
relevant to the development of fMRI-based biomarkers aiming at
individualized phenotype predictions. Machine error is expected to play
a non-negligible role in such analyses, even when predictions combine
results produced by multiple tools.

@@

\appendix

\begin{figure*}[ht]
  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
  \centering
  \includegraphics[width=\textwidth]{figures/replication-diffs.png}
  \caption{Differences between replicated and original results obtained in~\cite{bowring2019exploring} 
  of unthresholded group-level t-statistics for SPM (left) and AFNI (right).}
  \label{fig:replication-diff}
\end{minipage}}
\end{figure*}

\begin{figure*}[ht]
  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
    \begin{subfigure}[ht]{\textwidth}
      \centering
      \includegraphics[width=.6\textwidth]{figures/sbj-std-corr-unthresh-plot.png}
      %\caption{Standard deviation of thresholded t-statistics map on template surface}
    \end{subfigure}
    \caption{Voxel-wise comparison of BT and WT variabilty for 16 subjects.}
  \label{fig:unthresh-correlation-allsbj}
  \end{minipage}}
\end{figure*}

% No conclusion on which tool is more/less stable.

@@

>>>>

 \documentclass[11pt,onecolumn]{article}
 \usepackage[margin=0.5in]{geometry}

\usepackage[ruled,vlined]{algorithm2e}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage[binary-units=true]{siunitx}
\usepackage{ulem}
%\usepackage{censor}
\usepackage[table]{xcolor}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{tabularx}

@@

@@

\section{Results}
All scripts and data to reproduce the results are
available in out GitHub repository at \url{https://github.com/big-data-lab-team/fuzzy-neurotools}.

@@

We verified the correctness of our analyses by comparing our unperturbed
t-statistic group maps with the ones obtained
in~\cite{bowring2019exploring}. For FSL, we found
identical checksums. For SPM, the checksums were different but differences
were visually unnoticeable. For AFNI, the activation maps were similar
overall, however, differences were more noticeable visually. 
The observed differences remained small (see Appendix ~\ref{sec:supp-repro}) and might be due to the use of
Octave vs MATLAB in SPM and of multithreading in AFNI. We performed visual quality control of the AFNI
and SPM results for each individual subject and confirmed that \tristan{Ali: which ones?} images were
correctly registered to the MNI template.

\subsection{In group analysis, BT variability was larger than and correlated with machine error}

Table~\ref{table:pipeline-stats} reports on summary statistics for the
group-level t-statistics. For each tool pair (A, B), BT variability was
significantly larger than machine error in tool A or B, in both thresholded
and unthresholded maps (Wilcoxon signed-rank test p~\textless~$10^{-162}$
for all tests, t-test p=0 for all tests). These global differences were
confirmed regionally (Figure~\ref{fig:unthresh-maps}-\textbf{A},\textbf{B},\textbf{C}). 
In addition, BT and WT variability appeared moderately correlated (R
in [0.56, 0.58], p=0.0, Figure~\ref{fig:unthresh-maps}-\textbf{D}). Interestingly, the correlation 
was driven by a set of voxels exhibiting comparable BT and
WT values (located around the identity line in the XY plot), which, however, did not seem to have 
any spatial consistency.

\setlength{\tabcolsep}{5pt}
\begin{table}[h]
    \centering
    \begin{tabular}{cccccc|cc}
        \toprule
        && \multicolumn{4}{c|}{Group analyses} & \multicolumn{2}{c}{Subject analyses}\\
        \multirow{2}{*}{}& {} & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c|}{Unthresholded} & \multicolumn{2}{c}{Unthresholded} \\
        % \cmidrule{3-8}
        {} & {} & $\mu$ & $\sigma$ & $\mu$ & $\sigma$ & $\mu$ & $\sigma$ \\
        \midrule
        \rowcolor{lightgray!50}
        {Between Tools} & FSL vs. SPM        &  1.282       & 0.525      & 0.443     & 0.344  & 0.366       & 0.293     \\
        \rowcolor{lightgray!50}
        {(BT)} & FSL vs. AFNI                &  1.548       & 0.616      & 0.547     & 0.441  & 0.439       & 0.352     \\
        \rowcolor{lightgray!50} 
        {} & AFNI vs. SPM                    &  1.475       & 0.672      & 0.608     & 0.477  & 0.491       & 0.381     \\
        {Within Tool} & FSL                  &  0.354       & 0.491      & 0.082     & 0.065  & 0.077       & 0.054     \\
        {(WT)}   & SPM                       &  0.252       & 0.448      & 0.054     & 0.045  & 0.048       & 0.037     \\
        {}   & AFNI                          &  0.434       & 0.524      & 0.128     & 0.135  & 0.108       & 0.131     \\
        \bottomrule
    \end{tabular}
    \caption{Voxel-wise mean and standard deviation of BT and WT variability
    in group and subject t-statistics maps. \tristan{add stats on subject-level thresholded maps}}
    \label{table:pipeline-stats}
\end{table}

\begin{figure*}[ht]
  \centering
    % \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
      \begin{subfigure}[ht]{0.9\textwidth}
      \centering
      \includegraphics[width=0.9\textwidth]{figures/std/gl-unthresh.png}
      %\caption{Standard deviation of thresholded t-statistics map on template surface}
      \end{subfigure}
      \hfill
      \begin{subfigure}[ht]{0.9\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{figures/std-corr-unthresh-plot.png}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
      \end{subfigure}
    \caption{Unthresholded group-level variability computed between tools
    (\textbf{A}), within tools at machine error (\textbf{B}), difference
    between them (\textbf{C}), and voxel-wise comparison (\textbf{D}). }
    \label{fig:unthresh-maps}
    % \end{minipage}}
  \end{figure*}

  \subsection{In subject analyses, machine error approached BT variability in some regions}

  Table~\ref{table:pipeline-stats} also reports on summary statistics for subject-level unthresholded t-statistics maps. As for group-level
  maps, BT variability was consistently larger than WT variability (Wilcoxon
  signed-rank test p~\textless~$10^{-160}$ for all tests, t-test p=0 for all
  tests). However, for some subjects, machine error (WT variability) approached and even 
  surpassed BT in some regions (Figure~\ref{fig:unthresh-maps-sbj}).  As for the group maps, BT and WT variability appeared moderately
  correlated for all subjects (R in [0.442, 0.612], p=0.0 for all
  subjects, Appendix~\ref{sec:supp-subjects}).

  %%%%%%%%%% Var. of Unthresh sbj05%%%%%%%%
\begin{figure*}[ht]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/std/sbj05-std.png}
    %\caption{Standard deviation of thresholded t-statistics map on template surface}
    \caption{For subject with highest WT variability,
    unthresholded subject-level variability computed between tools (\textbf{A}), within tools at machine error (\textbf{B}),
     and difference between them (\textbf{C}).}
  \label{fig:unthresh-maps-sbj}
\end{figure*}

\subsection{At the precision t=17~bits, numerical variability approached BT variability in group analysis}

While the previous results were obtained for machine error, we also
evaluated numerical variability across different virtual precisions for FSL
and found that the virtual precision of t=17 bits minimized the RMSE
between BT and WT in unthresholded group maps. Figure~\ref{fig:gnp-mni} shows BT
and WT in the corresponding group maps obtained at t=17 bits, showing that
BT and WT reach comparable magnitudes in some regions. BT and WT remained
moderately correlated at this precision. \tristan{In the text, add statistics similar to Table 2.}

  %%%%%%%%%% plot different precisions%%%%%%%%
  \begin{figure*}[ht]
      \begin{subfigure}[ht]{\textwidth}
        \centering
        \includegraphics[width=.75\textwidth]{figures/bg_global_precision.pdf}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
        \end{subfigure}
        \hfill
        \begin{subfigure}[ht]{\textwidth}
          \centering
          \includegraphics[width=.8\textwidth]{figures/std-corr-unthresh-vp17-plot.png}
          %\caption{Standard deviation of thresholded t-statistics map on template surface}
        \end{subfigure}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
        \caption{Unthresholded group t-statistics standard deviations computed between tools (\textbf{A}),
          within tools at the virtual precision of t=17~bits (\textbf{B}), difference between them (\textbf{C}), and 
          voxel-wise comparison (\textbf{D}).}
    \label{fig:gnp-mni}
  \end{figure*}

  \subsection{Previous results are confirmed in thresholded group maps}

  Figure~\ref{fig:thresh-maps}-\textbf{A},\textbf{B},\textbf{C} compares BT
  and WT for thresholded group maps. Thresholding is an unstable operation
  that introduced high variability for both BT and WT at the edges of
  active regions. Except in these regions, BT remained consistently larger
  than WT. To measure a potential association between BT and WT, we
  measured WT instability and BT instability in each region of the
  HCP-MMP1.0 parcellation. The confusion matrices in
  Figure~\ref{fig:thresh-maps}-\textbf{D} report on such instabilities for
  the 360 tested regions. The average ratio of unstable regions was 26\%
  for BT and 9.2\% for WT, which confirmed that BT variability was larger than machine error.
  The average Cohen's kappa score between WT instability and BT instability was $\kappa=0.17$, indicating 
  a moderate agreement between WT instability and BT instability (-1 \textless $\kappa$ \textless 1, $\kappa$\leq 0 denotes chance agreement).

  %%%%%%%%%% Var. of Thresh %%%%%%%%
  \begin{figure*}[ht]
        \begin{subfigure}[ht]{\textwidth}
          \centering
          \includegraphics[width=\textwidth]{figures/std/gl-thresh.png}
          %\caption{Standard deviation of thresholded t-statistics map on template surface}
          \end{subfigure}
          \hfill
          \begin{subfigure}[ht]{\textwidth}
            \centering
            \includegraphics[width=.9\textwidth]{figures/dice_analysis-plot.png}
            %\caption{Standard deviation of thresholded t-statistics map on template surface}
          \end{subfigure}
        \centering
      \caption{Thresholded group t-statistics standard deviation maps
      computed across tools (\textbf{A}) and Fuzzy Libmath samples
      (\textbf{B}). The confusion matrices of activation instability
      in BT and WT among the 360 regions from the HCP-MMP1.0 parcellation is represented in the bottom row.}
      \label{fig:thresh-maps}
    \end{figure*}

@@

In fMRI group analyses, machine error remains an order of magnitude
smaller than between-tool variability. Group analyses have a regularization
effect toward numerical noise, which is expected to amplify as sample size
increases. Therefore, for fMRI studies with large sample sizes, machine
error can safely be neglected with respect to between-tool variability. The
recommendation made in~\cite{botvinik2020variability} to rely on ``multiverse" analyses where
multiple analysis tools are compared is therefore likely to successfully correct
for machine error in group studies.

@@

In subject analyses, machine error and between-tool variabilty can
become comparable for some subjects in some regions. This observation is particularly
relevant to the development of fMRI-based biomarkers aiming at
individualized phenotype predictions. Machine error is expected to play
a non-negligible role in such analyses, even when predictions combine
results produced by multiple tools.

@@

@@

\clearpage

\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{section}{0}

\makeatletter
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thesection}{S\arabic{section}}

\textbf{\centering \Large Supplemental Materials}

\section{Reproduced results}
\label{sec:supp-repro}

Figure~\ref{fig:replication-diff} shows the difference in SPM and AFNI
group analyses maps between the results in~\cite{bowring2019exploring} and
our replication. Numerical perturbations of 1 ulp are likely to have been
introduced by our replication due to the use of Octave vs MATLAB for SPM
and multithreading for AFNI. However, the group maps remained very similar
overall, which led us to conclude that our results correctly reproduced 
the ones in~\cite{bowring2019exploring}.
\begin{figure*}[ht]
  % \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
  % \centering
  \includegraphics[width=\textwidth]{figures/replication-diffs.png}
  \caption{Differences between reproduced and original results obtained in~\cite{bowring2019exploring} 
  of unthresholded group-level t-statistics for SPM (left) and AFNI (right).}
  \label{fig:replication-diff}
% \end{minipage}}
\end{figure*}

\section{BT and WT correlations for all subjects}
\label{sec:supp-subjects}

Figure~\ref{fig:unthresh-correlation-allsbj} plots the relationship between
WT and BT for each subject, showing a consistent moderate correlation between BT and
WT.

\begin{figure*}[ht]
      \centering
      \includegraphics[width=.6\textwidth]{figures/sbj-std-corr-unthresh-plot.png}
      \caption{Relationship between BT and WT variabilty for 16 subjects.}
  \label{fig:unthresh-correlation-allsbj}
\end{figure*}
